Characterization of gaps in directly bonded Si compound optics

### 2014-04-29 AO_bondedSi.tex
some tweaks

%The following 3 figures were made with fabry_perot_Si_20140421.pro and other variants.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

@@

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c c}
    \hline
    Name & Bonded/DSP & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    - & - & mm & mm & - & nm & - \\ 
        \hline
    VG01 & Bonded  & 100  &$1$ $\times$ 2 & None  & - &  \\
    VG02 & Bonded & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03 & Bonded & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & See Fig. \ref{figVG03pattern}\\    
    VG04 & Bonded & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15 & \\
    VG05 & DSP & 100 & 1&  - & - & Reference Sample  \\
    VG06 & DSP & 100 & 3.5 &  - & - & Reference Sample \\
    VG09 & Bonded & 75 & 1.5? & mesh C & 49 $\pm$6 & \\
    VG15 & Bonded & 100 & 1.5? &  mesh C, M, F  &14 $\pm$2 & \\
    VG17 & Bonded & 75 & 6.0? &  mesh C & 64 $\pm$6 nm & \\
    VS20 & Bonded & 100 & 1.5? &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}

>>>>

%The following 3 figures were made with fabry_perot_Si_20140421.pro and other variants.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  This curve is only accurate for normal incidence transmission.  Furthermore, the curve assumes the multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.}
\end{figure}

@@

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    VG01  & 100  &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & See Fig. \ref{figVG03pattern}\\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15 & \\
    VG09   & 75 & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}
